SIR Model With Testing Flows and Isolation

### 2020-12-09 codes/ali_test_sir.Rmd
working on ms
seperating functions

### Model
The model is
\begin{align}
\label{mod:1}
1)\ d S_u/dt &= -\Lambda S_u - F_S S_u + \omega S_n \\
2)\ d S_n/dt &= -\Lambda S_n + F_S S_u - \omega S_n \\
3)\ d I_u/dt &= \Lambda S_u - F_I I_u + \omega I_n  - \gamma I_u  \\
4)\ d I_n/dt &= \Lambda S_n + (1-p_I) F_I I_u - \omega I_n -\gamma I_n \\
5)\ d I_p/dt &= p_I F_I I_u - \omega I_p -\gamma I_p \\
6)\ d I_t/dt &= \omega I_p - \gamma I_t  \\
7)\ d R_u/dt &= \gamma I_u - F_R R_u + \omega R_n \\
8)\ d R_n/dt &= \gamma I_n + (1-p_R) F_R R_u - \omega R_n  \\
9)\ d R_p/dt &= \gamma I_p + p_R F_R R_u  - \omega R_p  \\
10)\ d R_t/dt&= \gamma I_t + \omega R_p  \\
11)\ dN/dt &= \omega (S_n + I_n + R_n)   \\
12)\ dP/dt &= \omega(I_p + R_p).
\end{align}

@@

```{r, model formulation}
sir.model <- function(time,state,params){
    unpack(as.list(c(state,params)))
    ## Force of Infection  
    Lambda <- beta * (I_u + eta_w*(I_n+I_p) + eta_c*I_t)/N0
    ## scaling the weights
    W <- W_S*S_u+W_I*I_u+W_R*R_u
    sigma <- rho*N0/W
    F_S <- sigma*W_S
    F_I <- sigma*W_I
    F_R <- sigma*W_R

    dS_u.dt <- -Lambda*S_u - (1-p_S) * F_S * S_u + omega * S_n
    dS_n.dt <- -Lambda*S_n + (1-p_S) * F_S * S_u - omega * S_n 
    dI_u.dt <-  Lambda*S_u + omega * I_n - F_I * I_u - gamma * I_u
    dI_n.dt <-  Lambda*S_n + (1-p_I) * F_I * I_u  - omega * I_n - gamma * I_n
    dI_p.dt <-  p_I * F_I * I_u - omega * I_p - gamma * I_p 
    dI_t.dt <-  omega * I_p - gamma * I_t 
    dR_u.dt <- gamma * I_u + omega * R_n - F_R * R_u  
    dR_n.dt <- gamma * I_n + (1-p_R) * F_R * R_u - omega * R_n
    dR_p.dt <- gamma * I_p + p_R * F_R * R_u - omega * R_p
    dR_t.dt <- gamma * I_t + omega * R_p
    dN.dt <- omega * (S_n + I_n + R_n)
    dP.dt <- omega *(I_p + R_p)

    # return the rate of change
  dxdt <- c(dS_u.dt,dS_n.dt,dI_u.dt,dI_n.dt,dI_p.dt,dI_t.dt,dR_u.dt,dR_n.dt,dR_p.dt,dR_t.dt,dN.dt,dP.dt)
    ## }
    return(list(dxdt))
}

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, #0.8, 1/3
             W_S=1, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_c=0.01, #isolation parameter 
            s=2 #eta_w/eta_c
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
# rootfun <- function (time, state,params) { 
#   unpack(as.list(c(state,params)))
#   return(I_u - 1) }
```

```{r DFE, message=FALSE}
# DFE; numerical approach
DFE <- function(S,params){
  S_u <- S[1]
  S_n <- S[2]
  I_u <-0
  R_u <-0
  unpack(as.list(params))
  W <- W_S*S_u+W_I*I_u+W_R*R_u
  sigma <- rho*N0/W
  F_S <- sigma*W_S

 return(c(eq1=S_u+S_n-N0,
          eq2=-F_S*S_u+omega*S_n))
}

roots_dfe <- multiroot(DFE, c(1, 1), parms = params, positive = T)
roots_dfe$root

# DFE; analytic approach
Sn_dfe <-function(params){
  unpack(as.list(params))
  return((rho*(1-p_S)*N0)/omega)
  }

Su_dfe<- params[["N0"]]-Sn_dfe(params)

state_dfe <- c(S_u=Su_dfe, S_n=Sn_dfe(params),
                I_u=0,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# check:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

# ggsave(p1_temp,filename = "R0contour_random.pdf" , path="../pix/")
ggsave(p1_temp,filename = "R0contour_TTI.pdf" , path="../pix/")

@@

```{r  chnages of R0 wrt omega,message=FALSE,warning=FALSE }
# R0_omega <- function(params){
#   unpack(as.list(params))
#          # a <- (eta_w-1)*W_I-(eta_c-1)*p_I*W_I
#          a <- ((s-p_I)*eta_c + (p_I-1))*W_I  #involving s
#          b <- 2*(eta_w-1)*gamma*W_S
#          c <- b*gamma/2
#          
#          d <- (-beta*rho)/(gamma*W_S*omega^2*(gamma+omega)^2)*(a*omega^2 + b*omega + c)
#          return(d)
# }
# 
# R0_omega(params)

@@

```{r }
 # specify the ranges
# if(F){
# beta  <- 0.5  ## set beta 
# gamma <- seq(0.1,0.5, length.out=n_out)
# p_I <- 0.9
# 
# # eta_w <- seq(0,1, length.out=n_out)
# eta_c <- seq(0.001,1, length.out=n_out)
# s <- seq(1,2,length.out=n_out)
# 
# rho <- seq(0,0.01, length.out=n_in)
# omega <- seq(0.011,2 , length.out=n_in) #note omega must be > rho, was 0.011
# 
# W_S <- 1/100
# W_I <- 1/3
# W_R <- 1/3
# 
#  df3_1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=gamma,omega=omega,rho=rho,
#                     W_S=W_S,W_I=W_I,W_R=W_R,
#                     p_S=params[["p_S"]],p_I=p_I,p_R=params[["p_R"]],
#                     eta_w=params[["eta_w"]],eta_c=eta_c,s=s)
# 
# df3_2 <- data.frame(df3_1,R0=apply(df3_1,1,function(params_in)R02(params=params_in)),
#                       R0_omega= apply(df3_1,1,function(params_in)R0_omega(params=params_in))
#                        )
# }
```

```{r show_contours_3, width=24,height=24,message=FALSE,warning=FALSE}
# if(F){
# p3 <- ggplot(df3_2,aes(x=omega,y=gamma,z=R0_omega))+ theme_bw() +
#     theme(panel.spacing=grid::unit(0,"lines"))
# (p3
#     + geom_contour_filled(breaks=pretty(unique(df3_2$R0_omega),5),
#                           alpha=0.5) ## breaks=0.2)
#     + geom_contour(breaks=0,alpha=0.5,colour="black")
#     + facet_grid(s~eta_c, labeller=label_special)
#     + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_fill_viridis_d(name=parse(text="dR[0]"))
# )
# }
```

>>>>

### Model

The model is
\begin{align}
\label{mod:1}
1)\ d S_u/dt &= -\Lambda S_u - F_S S_u + \omega S_n \\
2)\ d S_n/dt &= -\Lambda S_n + F_S S_u - \omega S_n \\
3)\ d I_u/dt &= \Lambda S_u - F_I I_u + \omega I_n  - \gamma I_u  \\
4)\ d I_n/dt &= \Lambda S_n + (1-p_I) F_I I_u - \omega I_n -\gamma I_n \\
5)\ d I_p/dt &= p_I F_I I_u - \omega I_p -\gamma I_p \\
6)\ d I_t/dt &= \omega I_p - \gamma I_t  \\
7)\ d R_u/dt &= \gamma I_u - F_R R_u + \omega R_n \\
8)\ d R_n/dt &= \gamma I_n + (1-p_R) F_R R_u - \omega R_n  \\
9)\ d R_p/dt &= \gamma I_p + p_R F_R R_u  - \omega R_p  \\
10)\ d R_t/dt&= \gamma I_t + \omega R_p  \\
11)\ dN/dt &= \omega (S_n + I_n + R_n)   \\
12)\ dP/dt &= \omega(I_p + R_p).
\end{align}

@@

source("SIRfunctions.R")
```

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, #0.8, 1/3
             W_S=1, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_c=0.01, #isolation parameter 
            s=2 #eta_w/eta_c
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
```

```{r DFE, message=FALSE}
# DFE; numerical approach
roots_dfe <- multiroot(DFE, c(1, 1), parms = params, positive = T)
roots_dfe$root

# DFE; analytic approach
Su <- Su_dfe(params)
Sn <- Sn_dfe(params)

state_dfe <- c(S_u=Su, S_n=Sn,
                I_u=0,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# check:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

## BMB: FIXME: probably wrong but ... ???
## ggsave(p1_temp,filename = "R0contour_random.pdf" , path="../pix/")
ggsave(p1_temp,filename = "R0contour_TTI.pdf" , path="../pix/")

@@

```{r  chnages of R0 wrt omega,message=FALSE,warning=FALSE }

@@
